A pipeline to analyse time-course gene expression data

### 2019-07-20 scripts/manuscript.Rmd
fix error in Rmd file

@@

```{r results="hide", echo=FALSE}
# Save the clustering for the GO term and pathway enrichment on the whole set
# of clusters.
kmeans_labels = as.data.frame(labels[!is.na(labels)])
write.table(kmeans_labels,
	    ".results/clustering_labels.txt",
	    sep="\t")
```

@@

# convert gene names
genes = getBM(attributes=c("ensembl_gene_id", "entrezgene"),
		filters="refseq_mrna", values=genes,
		mart=ensembl)["entrezgene"]
genes = as.vector(unlist(genes))
pathways = find_enriched_pathway(
    genes, species="mmu",
    download_latest=TRUE)$stastic

>>>>

- I get multiple errors in compilation of file. Not sure, however, why TravisCI didn't hit these problems, so you might want to see what's going on there. Probably caching or something, so might want to occassionally remove the cache and run again, if TravisCI is saving the cache. One error I fixed, but wasn't sure about this error (changed it to `entrezgene_id` and seems to be running now...):

```
label: enrichment_analysis (with options) 
List of 2
 $ results: chr "hide"
 $ message: logi FALSE

Quitting from lines 1124-1138 (manuscript.Rmd) 
Error in getBM(attributes = c("ensembl_gene_id", "entrezgene"), filters = "refseq_mrna",  : 
  Invalid attribute(s): entrezgene 
Please use the function 'listAttributes' to get valid attribute names
Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> getBM
```

@@

```{r results="hide", echo=FALSE}
# Save the clustering for the GO term and pathway enrichment on the whole set
# of clusters.
kmeans_labels = as.data.frame(labels[!is.na(labels)])
write.table(kmeans_labels,
	    "./results/clustering_labels.txt",
	    sep="\t")
```

@@

# convert gene names
genes = getBM(attributes=c("ensembl_gene_id", "entrezgene_id"),
		filters="refseq_mrna", values=genes,
		mart=ensembl)["entrezgene_id"]
genes = as.vector(unlist(genes))
pathways = find_enriched_pathway(
    genes, species="mmu",
    download_latest=TRUE)$stastic
